Approval and participation indexes for a voting process

### 2015-04-23 ApresentacoesArtigos/collectiveRanking/paper.tex
arrumacoes minimas

% \abbreviations{}
\abbreviations{PyPI, python package index}

@@

The approval index $\alpha_i$ and the participation index $\gamma_i$ of the proposal $i$ was defined as:
\begin{equation}
\begin{split}
\alpha_i=\frac{v^+_i-v^-_i}{\eta_i} \\
\gamma_i=\frac{v^+_i+v^-_i}{\eta_i}
\end{split}
\end{equation}
where $v^+_i$, $v^-_i$ and $\eta_i$ are approval count, disapproval count and exhibition count, respectively. Note that $\eta_i-v^+_i-v^-_i$ is the count the ``indifferent'' manifestations received by proposal $i$. Also, note that accepted sampling estimates error, $\eta_i$ is expected to be constant above a minimum threshold.

>>>>

% \abbreviations{}
%\abbreviations{PyPI, python package index}

@@

The approval index $\alpha_i$ and the participation index $\gamma_i$ of the proposal $i$ was defined as:
\begin{equation}
\begin{split}
\alpha_i=\frac{v^+_i-v^-_i}{\eta_i} \\
\gamma_i=\frac{v^+_i+v^-_i}{\eta_i}
\end{split}
\end{equation}
where $v^+_i$, $v^-_i$ and $\eta_i$ are approval count, disapproval count and exhibition count, respectively. Note that $\eta_i-v^+_i-v^-_i$ is the count of the ``indifferent'' manifestations received by proposal $i$. Also, note that accepted sampling estimates error, such indexes are expected to be constant above a minimum threshold.
